---
title: "conger"
output:
  pdf_document: 
    latex_engine: xelatex
  word_document: default
  html_document: default
---



```{r, initial setup, include = FALSE , fig.keep='all', fig.align="default"}
knitr::opts_chunk$set(warning = FALSE, echo=FALSE, message = FALSE)


library(ggplot2)
library(nlme)
library(tidyverse)
library(car)
library(stats)
library(MuMIn)
library(flextable)
library(emmeans)
library(ggplot2)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(ggspatial)
require(ggrepel)

load("./model_fits.RData")
conger <- conger %>% 
  mutate(region = str_replace(region, "Mittelmeer", "Mediterranean"),
         region = str_replace(region, "Atlantik", "Atlantic"))

conger.Cd <- conger.Cd %>% 
  mutate(region = str_replace(region, "Mittelmeer", "Mediterranean"),
         region = str_replace(region, "Atlantik", "Atlantic"))


hist(conger$Hg)
hist(conger$Pb)
hist(conger$Cd)


```


## Initial data inspection

```{r, fig.keep='all', fig.align="default", dpi = 300}

hist(conger$Hg, main = NULL, xlab = "Hg [µg/kg]")
hist(conger$Cd, main = NULL, xlab = "Cd [µg/kg]")
hist(conger$Pb, main = NULL, xlab = "Pb [µg/kg]")

ggplot(conger, aes(length)) + 
  geom_histogram(binwidth = 5, fill = "white", color = "black") +
  labs(x = "length [cm]")+
  facet_wrap(~station) +
  theme_bw()


```

**Fig 1** Overview of data distribution



## Plotting the model results

```{r, fig.keep='all', fig.align="default", dpi = 300}

ggplot(conger, aes(x=length, y=Hg)) +
  geom_point(size=0.9)+
  theme_bw()+
  geom_line(aes(x= length, y=predict(glm.Hg, type="response")), size = 0.3)+
  labs(x = "length [cm]", y = "Hg [µg/kg]")+
  facet_wrap(~ station)

ggplot(conger.Cd, aes(x=length, y=Cd)) +
  geom_point(size=0.9)+
  theme_bw()+
  geom_line(aes(x= length, y=predict(glm.Cd, type="response")), size = 0.3)+
  labs(x = "length [cm]", y = "Cd [µg/kg]")+
  facet_wrap(~ station)
 
ggplot(conger, aes(x=length, y=Pb)) +
  geom_point(size=0.9)+
  theme_bw()+
  geom_line(aes(x= length, y=predict(glm.Pb, type="response")), size = 0.3)+
  labs(x = "length [cm]", y = "Pb [µg/kg]")+
  facet_wrap(~ station)


```

**Fig 2a** Raw data and GLM predictions of contaminat levels in Conger per Station as panel



```{r, fig.keep='all', fig.align="default", dpi = 300}

fix_color <- (c("Al Hoceima" = "rosybrown", "Casablanca" = "tan4", "Laayoune Port" = "yellow3", "Martil" = "yellowgreen", "Nador" = "palegreen2", "Ras al Ma" = "paleturquoise3", "Safi" = "dodgerblue", "Sidi el Abed" = "mediumorchid1", "Skhirat" = "mediumvioletred"))

ggplot(conger, aes(x=length, y=Hg)) +
  geom_point(aes(col = station), size=2, alpha = 0.6)+
  theme_bw()+
  #geom_line(aes(x= length, y=predict(glm.Hg, type="response"), col = station, linetype = region), size = 0.3)+
  geom_line(aes(x= length, y=predict(glm.Hg, type="response"), col = station), size = 0.3)+
  scale_color_manual(values = fix_color)+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14),
        legend.text=element_text(size=12),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  labs(x = "length [cm]", y = "Hg [µg/kg WM]")
  #geom_hline(yintercept = 500, linetype = "dashed")

ggplot(conger.Cd, aes(x=length, y=Cd)) +
  geom_point(aes(col = station), size=2, alpha = 0.6)+
  theme_bw()+
  #geom_line(aes(x= length, y=predict(glm.Cd, type="response"), col = station, linetype = region), size = 0.3)+
  geom_line(aes(x= length, y=predict(glm.Cd, type="response"), col = station), size = 0.3)+
  scale_color_manual(values = fix_color)+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14),
        legend.text=element_text(size=12),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  labs(x = "length [cm]", y = "Cd [µg/kg WM]")

ggplot(conger, aes(x=length, y=Pb)) +
  geom_point(aes(col = station), size=2, alpha = 0.6)+
  theme_bw()+
  #geom_line(aes(x= length, y=predict(glm.Pb, type="response"), col = station, linetype = region), size = 0.3)+
  geom_line(aes(x= length, y=predict(glm.Pb, type="response"), col = station), size = 0.3)+
  scale_color_manual(values = fix_color)+
 theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14),
        legend.text=element_text(size=12),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  labs(x = "length [cm]", y = "Pb [µg/kg WM]")

ggplot(conger, aes(x=length, y=Hg)) +
  geom_point(aes(col = station), size=2, alpha = 0.6)+
  theme_bw()+
  #geom_line(aes(x= length, y=predict(glm.Hg, type="response"), col = station, linetype = region), size = 0.3)+
  geom_line(aes(x= length, y=predict(glm.Hg, type="response"), col = station), size = 0.3)+
  scale_color_manual(values = fix_color)+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14),
        legend.text=element_text(size=12),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none")+
  labs(x = "length [cm]", y = "Hg [µg/kg WM]")
  #geom_hline(yintercept = 500, linetype = "dashed")

ggplot(conger.Cd, aes(x=length, y=Cd)) +
  geom_point(aes(col = station), size=2, alpha = 0.6)+
  theme_bw()+
  #geom_line(aes(x= length, y=predict(glm.Cd, type="response"), col = station, linetype = region), size = 0.3)+
  geom_line(aes(x= length, y=predict(glm.Cd, type="response"), col = station), size = 0.3)+
  scale_color_manual(values = fix_color)+
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14),
        legend.text=element_text(size=12),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none")+
  labs(x = "length [cm]", y = "Cd [µg/kg WM]")

ggplot(conger, aes(x=length, y=Pb)) +
  geom_point(aes(col = station), size=2, alpha = 0.6)+
  theme_bw()+
  #geom_line(aes(x= length, y=predict(glm.Pb, type="response"), col = station, linetype = region), size = 0.3)+
  geom_line(aes(x= length, y=predict(glm.Pb, type="response"), col = station), size = 0.3)+
  scale_color_manual(values = fix_color)+
 theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14),
        legend.text=element_text(size=12),
        plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
       legend.position = "none")+
  labs(x = "length [cm]", y = "Pb [µg/kg WM]")

```

**Fig 2b** Raw data and GLM predictions of contaminat levels in COnger in single graph



**Tab 1** Model statistics, all values are provided on the log scale. 
Estimate for "station" provides the y-Intercept (i.e. contaminant load for a given station when length is 0) per station; significance indicates different from 0. 
Estimates of "station:length" provide the effect of length for this station (i.e. the change in contaminant load for an increase of one unit in length); significance indicates whether the effect is different from 0 at this station (i.e. the slope of contamination load over length at this station is significantly different from 0). 


```{r, fig.keep='all', fig.align="default"}

Hg <- as.data.frame(coef(summary(glm.Hg)))
Hg <- cbind(Hg_Coefficient = rownames(Hg), Hg)
rownames(Hg) <- NULL
Hg <- Hg %>% rename(std_error = 3,
                    t_value = 4,
                    p_value = 5) %>%
             mutate(Estimate = round(Estimate, 3),
                    std_error = round(std_error, 3),
                    t_value = round(t_value, 3),
                    p_value = round(p_value, 3)) 
            
Cd <- as.data.frame(coef(summary(glm.Cd)))
Cd <- cbind(Cd_Coefficient = rownames(Cd), Cd)
rownames(Cd) <- NULL
Cd <- Cd %>% rename(std_error = 3,
                    t_value = 4,
                    p_value = 5) %>%
             mutate(Estimate = round(Estimate, 3),
                    std_error = round(std_error, 3),
                    t_value = round(t_value, 3),
                    p_value = round(p_value, 3))

Pb <- as.data.frame(coef(summary(glm.Pb)))
Pb <- cbind(Pb_Coefficient = rownames(Pb), Pb)
rownames(Pb) <- NULL
Pb <- Pb %>% rename(std_error = 3,
                    t_value = 4,
                    p_value = 5) %>%
             mutate(Estimate = round(Estimate, 3),
                    std_error = round(std_error, 3),
                    t_value = round(t_value, 3),
                    p_value = round(p_value, 3))


flextable(Hg) %>% autofit()
flextable(Cd) %>% autofit()
flextable(Pb) %>% autofit()

```



**Tab 2** Pairwise comparisons between stations; significance indicates whether the effect of length differs between the two stations. 
Theoretically, when effect of length is stronger in one station compared to another then also the contaminant level should will be higher given that the "base" contamination load is equal between stations (i.e. all conger have the same contamination at length 0, the y-intercept). 
However, models perform better when "base" contamination is calculated separately per station (e.g. for Hg the calculated intercept ranges from  0.014 - 0.22 and differences are significant). Considering this value is far outside the observed range of data (starting around 60cm) they have little biological meaning; yet, especially when expressed per kg, differences in the "base" contamination are theoretically possible (particularly when expressed per kg) and thus we did not force the model thorgh the same y-Intercept to achieve the best fit to the empiric data. 
This does, however, require a more differentiated interpretation, since contamination is not solely explained by accumulation (i.e. as a function of length) at a given station, but also by differences in the "base" contamination.  

```{r, fig.keep='all', fig.align="default"}

Hg_trends <- emmeans(glm.Hg, specs = "station", var = "length")
#Hg.trends          # slope estimates and CIs
#pairs(Hg_trends)   # comparisons
Hg_pairs <- as.data.frame(pairs(Hg_trends))
Hg_pairs <- Hg_pairs %>% rename(contrast.Hg = contrast) %>% 
             mutate(estimate = round(estimate, 3),
                    SE = round(SE, 3),
                    t.ratio = round(t.ratio, 3),
                    p.value = round(p.value, 3))
  


Cd_trends <- emmeans(glm.Cd, specs = "station", var = "length")
#Cd.trends          # slope estimates and CIs
#pairs(Cd_trends)   # comparisons
Cd_pairs <- as.data.frame(pairs(Cd_trends))
Cd_pairs <- Cd_pairs %>% rename(contrast.Cd = contrast) %>% 
             mutate(estimate = round(estimate, 3),
                    SE = round(SE, 3),
                    t.ratio = round(t.ratio, 3),
                    p.value = round(p.value, 3))

Pb_trends <- emmeans(glm.Pb.nolength,"station")
#Pb.trends          # slope estimates and CIs
#pairs(Pb_trends)   # comparisons
Pb_pairs <- as.data.frame(pairs(Pb_trends))
Pb_pairs <- Pb_pairs %>% rename(contrast.Pb = contrast) %>% 
             mutate(estimate = round(estimate, 3),
                    SE = round(SE, 3),
                    t.ratio = round(t.ratio, 3),
                    p.value = round(p.value, 3))


flextable(Hg_pairs) %>% autofit()
flextable(Cd_pairs) %>% autofit()
flextable(Pb_pairs) %>% autofit()
```



## Comparing station averages

**Tab 3** Predictions of contamination at mean length of all congers (88.1cm)

```{r, fig.keep='all', fig.align="default"}

#make predictions for Hg and Pb
predictions <- expand.grid(station=unique(conger$station),
                     length=mean(conger$length))

predictions$Hg_at_length <- predict(glm.Hg, type="response", newdata = predictions)
predictions$Pb_at_length <- predict(glm.Pb, type="response", newdata = predictions)
predictions$Pb_mean <- predict(glm.Pb.nolength, type="response", newdata = predictions)

#seperate predictions for Cd due to different no of stations
predictions.Cd <- predictions[!(predictions$station=="Sidi el Abed"),]
predictions.Cd$Cd_at_length <- predict(glm.Cd, type="response", newdata = predictions.Cd)
predictions.Cd$Hg_at_length <- NULL
predictions.Cd$Pb_at_length <- NULL
predictions.Cd$Pb_mean <- NULL
predictions.Cd$length <- NULL

#calculate geometric means
geom_means <- conger %>%
                group_by(station) %>%
                summarize(geom_mean = exp(mean(log(Pb))),
                          mean = mean(Pb))

#merge both data frames
predictions <- left_join(predictions, predictions.Cd, by = "station")
predictions <- left_join(predictions, geom_means, by = "station")
rm(list = ls()[ls() %in% c("predictions.Cd", "geom_means")])

#round to one digit
predictions <- predictions %>% 
             mutate(length = round(length, 1),
                    Hg_at_length = round(Hg_at_length, 1),
                    Cd_at_length = round(Cd_at_length, 1),
                    Pb_at_length = round(Pb_at_length, 1),
                    Pb_mean = round(Pb_mean, 1),
                    Pb_geom_mean = round(geom_mean, 1)) %>%
                    relocate(Pb_mean, .after = Cd_at_length) %>%
                    relocate(Pb_at_length, .after = Cd_at_length)

predictions$geom_mean <- NULL
coordinates <- read.csv("coordinates_PAH.csv", header = T, sep  = ";")
predictions <- predictions %>% 
  left_join(coordinates, by = "station")
  

#Useful code if statistical comparisons should be done at a given length
#library(lsmeans)
#lsmeans(glm.Hg, pairwise ~ station | length, at = list(length = 81))

flextable(predictions %>% select(-Pb_at_length, -Pb_geom_mean, -lat, -long, -length, -Pb_mean, - X1OHPyr_mean, -mean)) %>%
  set_header_labels(Hg_at_length = "Hg [µg/kg WM]",
                    Cd_at_length = "Cd [µg/kg WM]") %>% 
  autofit()


```

```{r, fig.keep='all', fig.align="default", dpi = 300, message = FALSE, echo = FALSE, warning = FALSE}

theme_set(theme_bw())

land <- ne_download(scale = "medium", returnclass = "sf", type ="land", category = "physical")
ocean <- ne_download(scale = "medium", returnclass = "sf", type ="ocean", category = "physical")
morocco <- ne_countries(scale = "medium", returnclass = "sf", country = c("Mauritania", "Algeria"))
world <- ne_countries(scale = "medium", returnclass = "sf")


ggplot(data = predictions) +
  geom_sf(color = "black", fill = "oldlace", data = land) +
  geom_sf(color = "black", fill = "aliceblue", data = ocean) +
  # coord_sf(crs = "+init=epsg:3035")
  # coord_sf(crs = st_crs(3035)) + 
  annotation_scale(location = "bl", width_hint = 0.1, pad_y = unit(0.1, "in"), pad_x = unit(0.1, "in")) +
    annotation_north_arrow(location = "bl", which_north = "true", 
        pad_x = unit(0.03, "in"), pad_y = unit(0.2, "in"),
        style = north_arrow_fancy_orienteering) +
  coord_sf(xlim = c(30, -30.00), ylim = c(22.00, 65), expand = T) +
  geom_rect(mapping = aes(xmin = -15.5, xmax = -1, ymin = 25, ymax = 36.5), color = "black", alpha = 0)


ggplot(data = predictions) +
  geom_sf(color = "black", fill = "oldlace", data = land) +
  geom_sf(color = "gray55", fill = "oldlace", data = morocco) +
  geom_sf(color = "black", fill = "aliceblue", data = ocean) +
  # coord_sf(crs = "+init=epsg:3035")
  # coord_sf(crs = st_crs(3035)) + 
  annotation_scale(location = "tl", width_hint = 0.3, pad_y = unit(0.85, "in"), pad_x = unit(0.2, "in")) +
    annotation_north_arrow(location = "tl", which_north = "true", 
        pad_x = unit(0.48, "in"), pad_y = unit(0.15, "in"),
        style = north_arrow_fancy_orienteering) +
  geom_point (data = predictions, aes(x = long, y = lat), 
        shape = 15, size = 3.5, color = "black") +
  geom_text_repel(aes(label = station, x = long, y = lat), size = 3, max.overlaps = 100, 
                  nudge_x = ifelse(predictions$station == "Martil", 1, 
                            ifelse(predictions$station == "Ras al Ma", 0.7, 
                            ifelse(predictions$station == "Al Hoceima", -0.5, 
                            ifelse(predictions$station == "Sidi el Abed", 1.2, 1.2)))), 
                  nudge_y = ifelse(predictions$station == "Nador", 0.7, 
                            ifelse(predictions$station == "Martil", 0.6, 
                            ifelse(predictions$station == "Al Hoceima", -0.7, 
                            ifelse(predictions$station == "Ras al Ma", -0.7, -0.8)))), max.time = 1)+
  coord_sf(xlim = c(-1.00, -15.50), ylim = c(25.00, 36.50), expand = T) +
  theme(legend.key.size = unit(1.8, "cm"),
        legend.key.width = unit(0.3, "cm"),
        title = element_blank())


ggplot(data = predictions) +
  geom_sf(color = "black", fill = "oldlace", data = land) +
  geom_sf(color = "gray55", fill = "oldlace", data = morocco) +
  geom_sf(color = "black", fill = "aliceblue", data = ocean) +
  # coord_sf(crs = "+init=epsg:3035")
  # coord_sf(crs = st_crs(3035)) + 
  annotation_scale(location = "tl", width_hint = 0.3, pad_y = unit(0.85, "in"), pad_x = unit(0.2, "in")) +
    annotation_north_arrow(location = "tl", which_north = "true", 
        pad_x = unit(0.48, "in"), pad_y = unit(0.15, "in"),
        style = north_arrow_fancy_orienteering) +
  geom_point (data = predictions, aes(x = long, y = lat, fill = Hg_at_length), 
        shape = 21, size = 4.5, color = "black") +
  scale_fill_gradient(low ="white" , high = "navy" )+
  # geom_text_repel(aes(label = station, x = long, y = lat), size = 3, max.overlaps = 100, 
  #                 nudge_x = ifelse(predictions$station == "Martil", 1, 
  #                           ifelse(predictions$station == "Ras al Ma", 0.7, 
  #                           ifelse(predictions$station == "Al Hoceima", -0.5, 
  #                           ifelse(predictions$station == "Sidi el Abed", 1.2, 1.2)))), 
  #                 nudge_y = ifelse(predictions$station == "Nador", 0.7, 
  #                           ifelse(predictions$station == "Martil", 0.6, 
  #                           ifelse(predictions$station == "Al Hoceima", -0.7, 
  #                           ifelse(predictions$station == "Ras al Ma", -0.7, -0.8)))), max.time = 1)+
  coord_sf(xlim = c(-1.00, -15.50), ylim = c(25.00, 36.50), expand = T) +
  theme(legend.key.size = unit(1.8, "cm"),
        legend.key.width = unit(0.3, "cm"),
        title = element_blank())

ggplot(data = predictions) +
  geom_sf(color = "black", fill = "oldlace", data = land) +
  geom_sf(color = "gray55", fill = "oldlace", data = morocco) +
  geom_sf(color = "black", fill = "aliceblue", data = ocean) +
  # coord_sf(crs = "+init=epsg:3035")
  # coord_sf(crs = st_crs(3035)) + 
  annotation_scale(location = "tl", width_hint = 0.3, pad_y = unit(0.85, "in"), pad_x = unit(0.2, "in")) +
    annotation_north_arrow(location = "tl", which_north = "true", 
        pad_x = unit(0.48, "in"), pad_y = unit(0.15, "in"),
        style = north_arrow_fancy_orienteering) +
  geom_point (data = predictions %>% filter(!is.na(Cd_at_length)), aes(x = long, y = lat, fill = Cd_at_length), 
        shape = 21, size = 4.5, color = "black") +
  scale_fill_gradient(low ="aliceblue" , high = "darkred" )+
  # geom_text_repel(aes(label = station, x = long, y = lat), size = 3, max.overlaps = 100, 
  #                 nudge_x = ifelse(predictions$station == "Martil", 1, 
  #                           ifelse(predictions$station == "Ras al Ma", 0.7, 
  #                           ifelse(predictions$station == "Al Hoceima", -0.5, 
  #                           ifelse(predictions$station == "Sidi el Abed", 1.2, 1.2)))), 
  #                 nudge_y = ifelse(predictions$station == "Nador", 0.7, 
  #                           ifelse(predictions$station == "Martil", 0.6, 
  #                           ifelse(predictions$station == "Al Hoceima", -0.7, 
  #                           ifelse(predictions$station == "Ras al Ma", -0.7, -0.8)))), max.time = 1)+
  coord_sf(xlim = c(-1.00, -15.50), ylim = c(25.00, 36.50), expand = T)+
  theme(legend.key.size = unit(1.8, "cm"),
        legend.key.width = unit(0.3, "cm"),
        title = element_blank())


ggplot(data = predictions) +
  geom_sf(color = "black", fill = "oldlace", data = land) +
  geom_sf(color = "gray55", fill = "oldlace", data = morocco) +
  geom_sf(color = "black", fill = "aliceblue", data = ocean) +
  # coord_sf(crs = "+init=epsg:3035")
  # coord_sf(crs = st_crs(3035)) + 
  annotation_scale(location = "tl", width_hint = 0.3, pad_y = unit(0.85, "in"), pad_x = unit(0.2, "in")) +
    annotation_north_arrow(location = "tl", which_north = "true", 
        pad_x = unit(0.48, "in"), pad_y = unit(0.15, "in"),
        style = north_arrow_fancy_orienteering) +
  geom_point (data = predictions, aes(x = long, y = lat, fill = Pb_mean), 
        shape = 21, size = 4.5, color = "black") +
  scale_fill_gradient(low ="white" , high = "yellow4" )+
  # geom_text_repel(aes(label = station, x = long, y = lat), size = 3, max.overlaps = 100, 
  #                 nudge_x = ifelse(predictions$station == "Martil", 1, 
  #                           ifelse(predictions$station == "Ras al Ma", 0.7, 
  #                           ifelse(predictions$station == "Al Hoceima", -0.5, 
  #                           ifelse(predictions$station == "Sidi el Abed", 1.2, 1.2)))), 
  #                 nudge_y = ifelse(predictions$station == "Nador", 0.7, 
  #                           ifelse(predictions$station == "Martil", 0.6, 
  #                           ifelse(predictions$station == "Al Hoceima", -0.7, 
  #                           ifelse(predictions$station == "Ras al Ma", -0.7, -0.8)))), max.time = 1)+
  coord_sf(xlim = c(-1.00, -15.50), ylim = c(25.00, 36.50), expand = T)+
  theme(legend.key.size = unit(1.8, "cm"),
        legend.key.width = unit(0.3, "cm"),
        title = element_blank())

  
ggplot(data = predictions) +
  geom_sf(color = "black", fill = "oldlace", data = land) +
  geom_sf(color = "gray55", fill = "oldlace", data = morocco) +
  geom_sf(color = "black", fill = "aliceblue", data = ocean) +
  # coord_sf(crs = "+init=epsg:3035")
  # coord_sf(crs = st_crs(3035)) + 
  annotation_scale(location = "tl", width_hint = 0.3, pad_y = unit(0.85, "in"), pad_x = unit(0.2, "in")) +
    annotation_north_arrow(location = "tl", which_north = "true", 
        pad_x = unit(0.48, "in"), pad_y = unit(0.15, "in"),
        style = north_arrow_fancy_orienteering) +
  geom_point (data = predictions %>% filter(!is.na(X1OHPyr_mean)), aes(x = long, y = lat, fill = X1OHPyr_mean), 
        shape = 21, size = 4.5, color = "black") +
  scale_fill_gradient(low ="aliceblue" , high = "seagreen" )+
  # geom_text_repel(aes(label = station, x = long, y = lat), size = 3, max.overlaps = 100, 
  #                 nudge_x = ifelse(predictions$station == "Martil", 1, 
  #                           ifelse(predictions$station == "Ras al Ma", 0.7, 
  #                           ifelse(predictions$station == "Al Hoceima", -0.5, 
  #                           ifelse(predictions$station == "Sidi el Abed", 1.2, 1.2)))), 
  #                 nudge_y = ifelse(predictions$station == "Nador", 0.7, 
  #                           ifelse(predictions$station == "Martil", 0.6, 
  #                           ifelse(predictions$station == "Al Hoceima", -0.7, 
  #                           ifelse(predictions$station == "Ras al Ma", -0.7, -0.8)))), max.time = 1)+
  coord_sf(xlim = c(-1.00, -15.50), ylim = c(25.00, 36.50), expand = T)+
  theme(legend.key.size = unit(1.8, "cm"),
        legend.key.width = unit(0.3, "cm"),
        title = element_blank())
  

```
Mean concentration of contaminants at 88.1cm, as predicted by GLM in µg/kg wet mass (WM). Hg (blue), Cd (red), Pb (brown), 1OHPyr (green).   
\
\
**Tab 4** Sample numbers per heavy metal


```{r}
summary_n <- conger %>% 
  group_by(station) %>% 
  summarize (n_all = length(Hg),
             n_Cd = length(Cd[!is.na(Cd)]))

#CAREFUL! Shitty code, only works for this example
summary_n <- rbind(summary_n, (colSums(summary_n[c("n_Cd", "n_all")],))) %>% 
  mutate(station = str_replace(station, "108", "Total"))

flextable(summary_n)
```

