---
title: "conger"
output:
  pdf_document: 
    latex_engine: xelatex
  word_document: default
  html_document: default
---



```{r, initial setup, include = FALSE , fig.keep='all', fig.align="default"}
knitr::opts_chunk$set(echo=FALSE)

load("./models_fitted.RData")

library(ggplot2)
library(nlme)
library(tidyverse)
library(car)
library(stats)
library(MuMIn)
library(flextable)

hist(conger$Hg)
hist(conger$Pb)
hist(conger$Cd)


```


## Initial data inspection

```{r, fig.keep='all', fig.align="default"}

hist(conger$Hg, main = NULL, xlab = "Hg (µg/kg)")
hist(conger$Cd, main = NULL, xlab = "Cd (µg/kg)")
hist(conger$Pb, main = NULL, xlab = "Pb (µg/kg)")

ggplot(conger, aes(length)) + 
  geom_histogram(binwidth = 5, fill = "white", color = "black") + 
  facet_wrap(~station) +
  theme_bw()

```

**Fig 1** Overview of data distribution



## Plotting the model results

```{r, fig.keep='all', fig.align="default"}

ggplot(conger, aes(x=length, y=Hg)) +
  geom_point(size=0.9)+
  theme_bw()+
  geom_line(aes(x= length, y=predict(glm.Hg, type="response")), size = 0.3)+
  labs(x = "length (cm)", y = "Hg (µg/kg)")+
  facet_wrap(~ station)

ggplot(conger.Cd, aes(x=length, y=Cd)) +
  geom_point(size=0.9)+
  theme_bw()+
  geom_line(aes(x= length, y=predict(glm.Cd, type="response")), size = 0.3)+
  labs(x = "length (cm)", y = "Cd (µg/kg)")+
  facet_wrap(~ station)
 
ggplot(conger, aes(x=length, y=Pb)) +
  geom_point(size=0.9)+
  theme_bw()+
  geom_line(aes(x= length, y=predict(glm.Pb, type="response")), size = 0.3)+
  labs(x = "length (cm)", y = "Pb (µg/kg)")+
  facet_wrap(~ station)


```

**Fig 2a** Raw data and GLM predictions of contaminat levels in COnger per Station as panel



```{r, fig.keep='all', fig.align="default"}
ggplot(conger, aes(x=length, y=Hg)) +
  geom_point(aes(col = station), size=0.9)+
  theme_bw()+
  geom_line(aes(x= length, y=predict(glm.Hg, type="response"), col = station, linetype = region), size = 0.3)+
  labs(x = "length (cm)", y = "Hg (µg/kg)")+
  geom_hline(yintercept = 0.5, linetype = "dashed")

ggplot(conger.Cd, aes(x=length, y=Cd)) +
  geom_point(aes(col = station), size=0.9)+
  theme_bw()+
  geom_line(aes(x= length, y=predict(glm.Cd, type="response"), col = station, linetype = region), size = 0.3)+
  labs(x = "length (cm)", y = "Cd (µg/kg)")

ggplot(conger, aes(x=length, y=Pb)) +
  geom_point(aes(col = station), size=0.9)+
  theme_bw()+
  geom_line(aes(x= length, y=predict(glm.Pb, type="response"), col = station, linetype = region), size = 0.3)+
  labs(x = "length (cm)", y = "Pb (µg/kg)")

```

**Fig 2b** Raw data and GLM predictions of contaminat levels in COnger in single graph



**Tab 1** Model statistics. Coefficients give the mean contamination at mean length of all congers on the log scale (i.e. exp of estimate provides the\ values given in Tab 2). p-values (last column, now header) indicate whether they are different from 0.\
Coefficients with the suffix ":scale(length..." give the slope for the respective station. p-values (last column, no header) indicate whether\  
the slopes are significant (i.e. different from 0).

```{r, fig.keep='all', fig.align="default"}


Hg <- as.data.frame(coef(summary(glm.Hg)))
Hg <- cbind(Hg_Coefficient = rownames(Hg), Hg)
rownames(Hg) <- NULL
Hg <- Hg %>% rename(std_error = 3,
                    t_value = 4,
                    p_value = 5) %>%
             mutate(Estimate = round(Estimate, 3),
                    std_error = round(std_error, 3),
                    t_value = round(t_value, 3),
                    p_value = round(p_value, 3)) 
            
Cd <- as.data.frame(coef(summary(glm.Cd)))
Cd <- cbind(Cd_Coefficient = rownames(Cd), Cd)
rownames(Cd) <- NULL
Cd <- Cd %>% rename(std_error = 3,
                    t_value = 4,
                    p_value = 5) %>%
             mutate(Estimate = round(Estimate, 3),
                    std_error = round(std_error, 3),
                    t_value = round(t_value, 3),
                    p_value = round(p_value, 3))

Pb <- as.data.frame(coef(summary(glm.Pb)))
Pb <- cbind(Pb_Coefficient = rownames(Pb), Pb)
rownames(Pb) <- NULL
Pb <- Pb %>% rename(std_error = 3,
                    t_value = 4,
                    p_value = 5) %>%
             mutate(Estimate = round(Estimate, 3),
                    std_error = round(std_error, 3),
                    t_value = round(t_value, 3),
                    p_value = round(p_value, 3))

flextable(Hg) %>% autofit()
flextable(Cd) %>% autofit()
flextable(Pb) %>% autofit()

```



**Tab 2** Pairwise comparisons between stations

```{r, fig.keep='all', fig.align="default"}

library("lsmeans")

Hg_trends <- lstrends(glm.Hg, ~ station, var = "length")
#Hg.trends          # slope estimates and CIs
#pairs(Hg_trends)   # comparisons
Hg_pairs <- as.data.frame(pairs(Hg_trends))
Hg_pairs <- Hg_pairs %>% rename(contrast.Hg = contrast) %>% 
             mutate(estimate = round(estimate, 3),
                    SE = round(SE, 3),
                    z.ratio = round(z.ratio, 3),
                    p.value = round(p.value, 3))
  


Cd_trends <- lstrends(glm.Cd, ~ station, var = "length")
#Cd.trends          # slope estimates and CIs
#pairs(Cd_trends)   # comparisons
Cd_pairs <- as.data.frame(pairs(Cd_trends))
Cd_pairs <- Cd_pairs %>% rename(contrast.Cd = contrast) %>% 
             mutate(estimate = round(estimate, 3),
                    SE = round(SE, 3),
                    z.ratio = round(z.ratio, 3),
                    p.value = round(p.value, 3))

Pb_trends <- lstrends(glm.Pb, ~ station, var = "length")
#Pb.trends          # slope estimates and CIs
#pairs(Pb_trends)   # comparisons
Pb_pairs <- as.data.frame(pairs(Pb_trends))
Pb_pairs <- Pb_pairs %>% rename(contrast.Pb = contrast) %>% 
             mutate(estimate = round(estimate, 3),
                    SE = round(SE, 3),
                    z.ratio = round(z.ratio, 3),
                    p.value = round(p.value, 3))

flextable(Hg_pairs) %>% autofit()
flextable(Cd_pairs) %>% autofit()
flextable(Pb_pairs) %>% autofit()
```



## Comparing station averages

**Tab 3** Predictions of contamination at mean length (or mean for Pb)

```{r, fig.keep='all', fig.align="default"}

#make predictions for Hg and Pb
predictions <- expand.grid(station=unique(conger$station),
                     length=mean(conger$length))

predictions$Hg_at_length <- predict(glm.Hg, type="response", newdata = predictions)
predictions$Pb_mean <- predict(glm.Pb.nolength, type="response", newdata = predictions)

#seperate predictions for Cd due to different no of stations
predictions.Cd <- predictions[!(predictions$station=="Sidi el Abed"),]
predictions.Cd$Cd_at_length <- predict(glm.Cd, type="response", newdata = predictions.Cd)
predictions.Cd$Hg_at_length <- NULL
predictions.Cd$Pb_mean <- NULL
predictions.Cd$length <- NULL

#calculate geometric means
geom_means <- conger %>%
                group_by(station) %>%
                summarize(geom_mean = exp(mean(log(Pb))))

#merge both data frames
predictions <- left_join(predictions, predictions.Cd, by = "station")
predictions <- left_join(predictions, geom_means, by = "station")
rm(list = ls()[ls() %in% c("predictions.Cd", "geom_means")])

#round to one digit
predictions <- predictions %>% 
             mutate(length = round(length, 1),
                    Hg_at_length = round(Hg_at_length, 1),
                    Cd_at_length = round(Cd_at_length, 1),
                    Pb_mean = round(Pb_mean, 1),
                    Pb_geom_mean = round(geom_mean, 1)) %>%
                    relocate(Pb_mean, .after = Cd_at_length)

predictions$geom_mean <- NULL

#Useful code if statistical comparisons should be done at a given length
#library(lsmeans)
#lsmeans(glm.Hg, pairwise ~ station | length, at = list(length = 81))

flextable(predictions) %>% autofit()


```

